Toward a Comparable Corpus of Latvian, Russian and English Tweets

### 2017-05-22 paper.tex
Minor

The properties of the corpus correspond to the expectation to reflect the real world events and language use proportion, but its size is too small to draw solid conclusions. However, the construction of a reliable comparable corpus is a matter of the data collection procedure and corpus' application, because, as this study shows, not all topics are discussed equally.

@@

To illustrate the language usage pattern between multilingual users, their first most frequently used language, their second most frequently used language and their third most frequently language were identified. If a user tweeted equally in two (three) languages, then the two (three) languages were given the maximal preference. A user who tweeted equally in Latvian and Russian, but less in English, will be counted as Latvian and Russian being their first preference, English as the third.

>>>>

The properties of the corpus correspond to the expectation that it will reflect the real world events and language use proportion, but its size is too small to draw solid conclusions. However, the construction of a reliable comparable corpus is a matter of the data collection procedure and corpus' application, because, as this study shows, not all topics are discussed equally.

@@

To illustrate the language usage pattern between multilingual users, their first most frequently used language, their second most frequently used language and their third most frequently language were identified. If a user tweeted equally in two (three) languages, then the two (three) languages were given the maximal preference. A user who tweeted equally in Latvian and Russian, but less in English, is counted as Latvian and Russian being their first preference, English as the third.
